Do fast stellar centroiding methods saturate the Cram\'{e}r-Rao lower bound?

### 2016-09-26 ms/ms.tex
clarification of CRLB and the Gaussian noise assumption, dropping the word accuracy

In order to test the accuracy of various centroiding methods, we need to compare their 
performances against each other at saturating the Cram\'{e}r-Rao lower bound on centroiding error. 
The closer an estimator is to saturating the CRLB, the more information about the quantity that we 
need to estimate is preserved. The closer the root-mean-squared-error of a given estimator is to the bound, 
the more optimal the estimator is.

@@

\begin{itemize}
  \item Known, constant model observable with known dependence on the model parameters. 
        In this work the model observables are the presumed known Moffat PSF profiles, 
        and the model parameters are the centroids. 
  \item Known, stationary noise process. In the context of centroiding stars, this is equivalent to 
        having background limited nosie from sky background and CCD readout noise.
  \item Uncorrelated Gaussian noise with no outliers. 
\end{itemize}

>>>>

The closer an estimator is to saturating the CRLB, the more information about the quantity that we 
need to estimate is preserved. The closer the root-mean-squared-error of a given estimator is to the bound,  
the more optimal---in terms of preseving the information---the estimator is. In order to test how information-preserving 
various centroiding methods are, we need to compare their 
performances against each other at saturating the Cram\'{e}r-Rao lower bound 
on centroiding error.

@@

\begin{itemize}
  \item Known, constant model observable with known dependence on the model parameters. 
        In this work the model observables are the presumed known Moffat PSF profiles, 
        and the model parameters are the centroids. 
  \item Known, stationary noise process. In the context of centroiding stars, this is equivalent to 
        having background limited noise from sky background and CCD readout noise.
  \item Uncorrelated Gaussian noise with no outliers. 
\end{itemize}

We note that the conditions of stationary noise process and uncorrelated Gaussian noise,  may not be representive of many realistic scenarios. 
For instance, in a situation where there is substantial contribution from instruement gain---more effective for the 
bright sources---to the noise, the last two conditions are not met. In this study however, we are only going to consider relatively faint stars, 
for which the assumption of a Gaussian background noise is valid.
